Contextual Identity: A Framework for Usable Privacy

### 2012-10-13 paper.tex
ispell

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online enviroments~\cite{delete}. Thus, managing contextual identities
online has become increasingly difficult and fraught with mistakes.

@@

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogenous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

@@

\section{Discussion}
People have multiple contextual identities. Sharing personal information in
those contexts is a great way to foster postive human interaction.  We hope
that contextual identity will serve as a framework for both developers to
understand their users' privacy needs, and to develop tools that allow users to
act in their contextual identities in a spontaneous, relaxed, and interesting
way.

>>>>

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online environments~\cite{delete}. Thus, managing contextual identities
online has become increasingly difficult and fraught with mistakes.

@@

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogeneous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

@@

\section{Discussion}
People have multiple contextual identities. Sharing personal information in
those contexts is a great way to foster positive human interaction.  We hope
that contextual identity will serve as a framework for both developers to
understand their users' privacy needs, and to develop tools that allow users to
act in their contextual identities in a spontaneous, relaxed, and interesting
way.
